Cloudbreak: A MapReduce Algorithm for Detecting Genomic Structural Variation

### 2013-02-27 manuscript/manuscript.tex
brew latex tables

\begin{table}[t]
\begin{center}
\begin{tabular}{rrrrrr}
  \hline
 & 40-100bp  & 101-250bp  & 251-500bp & 501-1000bp & $>$ 1000bp \\ 
 Total Number & 224 & 84 & 82 & 31 & 26 \\ 
  \hline
Cloudbreak &  51 (10) &  51 (\textbf{3}) &  \textbf{55} (\textbf{5}) &  \textbf{12} (\textbf{4}) &  \textbf{15} (\textbf{1}) \\ 
  Breakdancer &  \textbf{52} (14) &  49 (2) &  49 (0) &  7 (0) &  14 (0) \\ 
  GASVPro &  31 (4) &  25 (0) &  23 (0) &  2 (0) &  6 (0) \\ 
  DELLY &  22 (2) &  \textbf{55} (2) &  40 (0) &  8 (0) &  12 (0) \\ 
  Pindel &  29 (\textbf{16}) &  11 (0) &  21 (0) & 1 (0) &  8 (0) \\ 
   \hline
\end{tabular}
\end{center}
\caption{The number of simulated deletions in the 30X diploid chromosome 2 with Venter deletions found by each tool at a 10\% FDR, as well as the number of those deletions that were discovered exclusively by each tool (in parentheses). The total number of deletions in each size class in the true set of deletions is shown in the second row of the header.}
\label{chr2preds}
\end{table}

@@

\begin{table}[b]
\begin{center}
\begin{tabular}{rrr|rr}
 & \multicolumn{2}{c}{Simulated Data} & \multicolumn{2}{c}{NA18507} \\
\hline
 &  Non-repeat & Repeat  &  Non-repeat & Repeat \\ 
 Total Number & 122 & 317 & 604 & 10,321 \\ 
  \hline
Cloudbreak & \textbf{29} (4) & \textbf{155} (\textbf{19}) & \textbf{204} (\textbf{38}) & \textbf{761} (158) \\ 
  Breakdancer &  \textbf{29} (\textbf{6}) & 142 (10) & 186 (25) & 751 (42) \\ 
  GASVPro & 15 (2) & 72 (2) & 71 (5) & 264 (8) \\ 
  DELLY & 21 (2) & 116 (2) & 147 (12) & 618 (11) \\ 
  Pindel & 8 (4) & 62 (12) & 98 (26) & 563 (\textbf{264}) \\ 
   \hline
\end{tabular}
\end{center}
\caption{Detected deletions on the simulated and NA18507 data sets identified by each tool, broken down by whether the deletion overlaps with a RepeatMasker-annotated element.}
\label{repmaskpreds}
\end{table}

>>>>

\begin{table}[t]
\begin{center}
\begin{tabular}{rrrrrr}
  \hline
 & 40-100bp  & 101-250bp  & 251-500bp & 501-1000bp & $>$ 1000bp \\ 
 Total Number & 224 &  84 & 82 &  31 & 26\\ 
  \hline
  Cloudbreak  & 51 (10)  & 51 (\textbf{3}) &  \textbf{55} (\textbf{5}) & \textbf{12} (\textbf{4}) & \textbf{15} (\textbf{1}) \\ 
  Breakdancer & \textbf{52} (14)  & 49 (2) &  49 (0) & 7 (0) & 14 (0) \\ 
  GASVPro     & 31 (4)  & 25 (0) &  23 (0) & 2 (0) & 6 (0) \\ 
  DELLY       & 22 (2)  & \textbf{55} (2) &  40 (0) & 8 (0) & 12 (0) \\ 
  Pindel      & 29 (\textbf{16})  & 11 (0) &  21 (0) & 1 (0) & 8 (0)\\ 
   \hline
\end{tabular}
\end{center}
\caption{The number of simulated deletions in the 30X diploid chromosome 2 with Venter deletions found by each tool at a 10\% FDR, as well as the number of those deletions that were discovered exclusively by each tool (in parentheses). The total number of deletions in each size class in the true set of deletions is shown in the second row of the header.}
\label{chr2preds}
\end{table}

@@

\begin{table}[b]
\begin{center}
\begin{tabular}{rrr|rr}
 & \multicolumn{2}{c}{Simulated Data} & \multicolumn{2}{c}{NA18507} \\
\hline
 &  Non-repeat & Repeat  &  Non-repeat & Repeat \\ 
 Total Number & 120 & 327 & 553 & 7851 \\ 
  \hline
  Cloudbreak  & \textbf{29} (4) & \textbf{155} (\textbf{19}) & \textbf{204} (\textbf{38}) & \textbf{761} (158) \\ 
  Breakdancer & \textbf{29} (\textbf{6}) & 142 (10) & 186 (25) & 751 (42) \\
  GASVPro     & 15 (2) & 72 (2) & 71 (5) & 264 (8) \\
  DELLY       & 21 (2) & 116 (2) & 147 (12) & 618 (11) \\
  Pindel      & 8 (4) & 62 (12) & 98 (26) & 563 (\textbf{264}) \\ 
   \hline
\end{tabular}
\end{center}
\caption{Detected deletions on the simulated and NA18507 data sets identified by each tool, broken down by whether the deletion overlaps with a RepeatMasker-annotated element.}
\label{repmaskpreds}
\end{table}
